Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

>>>>

This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which " underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:

1 Beliefs  
2 Attitudes  
3 Intentions  
4 Behaviour

There could even be an incidence of the intention to perform a certain behaviour and the actual performance of that behaviour, which could lead to look into skills, abilities and willpower. It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ????? Boyd and Vosikis MAIN BIB ????? but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality.
